An Open Platform for Managing Short Programming Exercises

### 2013-06-22 paper/paper.tex
another minor phrasing tweak

Setting up a CloudCoder instance requires two Linux servers: one to
host the web application and database, and another to build and
test the student submissions.  The installation process is reasonably well
automated, and can be completed by someone comfortable with
running Linux commands on remote servers in about an hour.
We have received one report of a user successfully installing CloudCoder
without assistance.  However, self-hosting is still a significant
barrier to adoption, and we are investigating ways to make it
easier for potential users to adopt CloudCoder.

>>>>

Setting up a CloudCoder instance requires two Linux servers: one to
host the web application and database, and another to build and
test the student submissions.  The installation process is reasonably well
automated, and can be completed by someone comfortable with
running Linux commands on remote servers in less than one hour.
We have received one report of a user successfully installing CloudCoder
without assistance.  However, self-hosting is still a significant
barrier to adoption, and we are investigating ways to make it
easier for potential users to adopt CloudCoder.
